---
title: "ISSPxVTS_v1 analysis - V2 [addressing Kerstin's comments]"
author: "Yu-Chin Chiu"
date: "October 6, 2017"
output: md_document
---

```{r knitSetup}
knitr::opts_chunk$set(fig.width=6, fig.height=4, fig.path='figure/', echo = FALSE, warning = FALSE, message = FALSE)

```

#### First, Set up the environment and load the data: validgpData.csv 
This file came from python scripts - cleaning and preprocessing

```{r setup}
rm(list=ls())
library('tidyverse')
library('ez')

currentDir <- getwd()
dataDir <- "C:/Users/yc180/Documents/YCCProjects/ISSPxVTS_v1/"
setwd(dataDir)

#gpData=read_csv('gpData_v2.csv',col_names=TRUE) # all subjects data, none excluded

gpData = read_csv('validgpData_v1.csv',col_names=TRUE) # good subjects data, N=44

setwd(currentDir)
source("getWSSE.R")

```
#### Set up some formating for the plots
Set up some good format, here I am using apatheme with white background, with black axis lines, no grids.
```{r fig apa-format}
apatheme = theme_bw()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line=element_line())
dodge = position_dodge(width=0.9)
```

```{r analysis_prep}
# Turn a bunch of codings into categorical factors
catVblList <- c("bkType", "task", "swProb", "trialType", "runId", "runId_half","sbjId")
idx <- match(catVblList, colnames(gpData))
for (c in idx[!is.na(idx)]){
  gpData[[c]] <- factor(gpData[[c]], ordered = TRUE)
}
gpData$bkType <- factor(gpData$bkType, levels = c("cued", "choice"), ordered=TRUE)
gpData[gpData$sbjACC==0, "sbjRT"] <- NA
NrS <- length(unique(gpData$sbjId))

```
#### First summarize individual subject's data

```{r within-Subject analysis}
gpCondM1 <- tibble()
gpCondM2 <- tibble()
gpCondM3 <- tibble()
gpCondM4 <- tibble()
gpCondM5 <- tibble()
gpData$taskNum = gpData$taskNum-1

for (S in unique(gpData$sbjId)) {
  mydata <-  gpData %>% filter(sbjId==S) 
  
  # 2 bkType (cued, choice) x 2 swProb (25%, 75%) x 2 trial type (switch, repeat)
  condM <- mydata %>%
    group_by(bkType, swProb, trialType) %>% 
    summarise(meanRT = mean(sbjRT, na.rm = TRUE), meanACC = mean(sbjACC))
  condM <- bind_cols(tibble(sbjId = rep(S,dim(condM)[1])), condM)
  ISSP <- condM[2,"meanRT"] - condM[1,"meanRT"] - (condM[4,"meanRT"]-condM[3,"meanRT"])
  ISSP_choice <- condM[6,"meanRT"] - condM[5,"meanRT"] - (condM[8,"meanRT"]-condM[7,"meanRT"])
  gpCondM1 <- bind_rows(gpCondM1, condM)
  
  
  # choice: switch Rate as a function of swProb
  condM2 <- mydata %>% 
    filter(bkType=="choice") %>%
    group_by(swProb) %>%
    summarise(swRate = mean(trialType2, na.rm = TRUE), tskRatio = mean(taskNum))
  condM2 <- bind_cols(tibble(sbjId = rep(S,dim(condM2)[1])), condM2)
  gpCondM2 <- bind_rows(gpCondM2, condM2)
  
  # choice: 2 runs 
  condM3 <- mydata %>% 
    filter(bkType=="choice") %>%
    group_by(runId, swProb) %>%
    summarise(swRate = mean(trialType2, na.rm = TRUE), tskRatio = mean(taskNum))
  condM3 <- bind_cols(tibble(sbjId = rep(S,dim(condM3)[1])), condM3)
  gpCondM3 <- bind_rows(gpCondM3, condM3)
  
  #choice: 4 runs
  condM4 <- mydata %>%
    filter(bkType=="choice") %>%
    group_by(runId_half, swProb) %>%
    summarise(swRate = mean(trialType2, na.rm=TRUE), tskRatio = mean(taskNum))
  condM4 <- bind_cols(tibble(sbjId = rep(S,dim(condM4)[1])), condM4)
  gpCondM4 <- bind_rows(gpCondM4, condM4)
    
  
  # task biases
  condM5 <- mydata %>%
    group_by(bkType, swProb) %>% 
    summarise(tskRatio = mean(taskNum))
  condM5 <- bind_cols(tibble(sbjId = rep(S,dim(condM5)[1])), condM5)
  gpCondM5 <- bind_rows(gpCondM5, condM5)



  

}

```
#### Then, calculate the group mean and within-subject SEM using "getWSSE" (a function I wrote)
```{r ISSP analysis}

df <- gpCondM1 %>% select(-meanACC)
colnames(df)[colnames(df)=="meanRT"] <- "M"
LnMSE_rt <- getWSSE(df)


df <- gpCondM1 %>% select(-meanRT)
colnames(df)[colnames(df)=="meanACC"] <- "M"
LnMSE_acc <- getWSSE(df)


ISSP <- gpCondM1 %>%
  group_by(bkType, swProb, trialType) %>% 
  summarise(gpmeanRT = mean(meanRT), SE_rt = LnMSE_rt , gpmeanACC = mean(meanACC)*100, SE_acc = LnMSE_acc*100) 

swCost_75 = ISSP[4,"gpmeanRT"]-ISSP[3,"gpmeanRT"]
swCost_25 = ISSP[2,"gpmeanRT"]-ISSP[1,"gpmeanRT"]

print('Group means:')

print(paste("cued: swCost:75% =", sprintf("%.2f", swCost_75), "ms"))
print(paste("cued: swCost:25% =", sprintf("%.2f", swCost_25), "ms"))

VTSswCost_75 = ISSP[8,"gpmeanRT"]-ISSP[7,"gpmeanRT"]
VTSswCost_25 = ISSP[6,"gpmeanRT"]-ISSP[5,"gpmeanRT"]

print(paste("choice: swCost:75% =", sprintf("%.2f", VTSswCost_75), "ms"))
print(paste("choice: swCost:25% =", sprintf("%.2f", VTSswCost_25), "ms"))


```
### RESULTS: 
#### Figure 1: ISSP(swProb x trialtype) effect in **RT** by block type (cued vs. choice) 
```{r Figure1}

ISSP %>%
  ggplot(aes(x=swProb, y = gpmeanRT, fill = trialType)) + 
  geom_col(position = dodge) + 
  geom_errorbar(aes(ymax = gpmeanRT + (1*SE_rt), ymin =gpmeanRT -(1*SE_rt)), position = dodge, width=.25) + facet_grid(.~bkType) + 
  ylab("mean RT (correct trials)") + 
  coord_cartesian(ylim = c(600,900)) +
  scale_fill_grey()

```

#### 3-way ANOVA: RT ~ 2 bkType x 2 swProb x 2 trialType

```{r}
z = ezANOVA(data = gpCondM1
            , dv = meanRT
            , wid = sbjId
            , within = .(bkType, swProb, trialType)
            , within_full = .(bkType, swProb, trialType)
            , type = 3
            , detailed = TRUE)
print(z)

```
#### 2-way ANOVA: RT ~ 2 swProb x 2 trialType [cued condition only]
```{r}
z = ezANOVA(data = gpCondM1[gpCondM1$bkType=="cued",]
            , dv = meanRT
            , wid = sbjId
            , within = .(swProb, trialType)
            , within_full = .(swProb, trialType)
            , type = 3
            , detailed = TRUE)
print(z)

```
#### 2-way ANOVA: RT ~ 2 swProb x 2 trialType [choice condition only]
```{r}
z = ezANOVA(data = gpCondM1[gpCondM1$bkType=="choice",]
            , dv = meanRT
            , wid = sbjId
            , within = .(swProb, trialType)
            , within_full = .(swProb, trialType)
            , type = 3
            , detailed = TRUE)
print(z)

```
#### Figure 2: ISSP(swProb x trialtype) effect in **accuracy** by block type (cued vs. choice) 
```{r Figure2}
ISSP %>%
  ggplot(aes(x=swProb, y = gpmeanACC, fill = trialType)) + 
  geom_col(position = dodge) + 
  geom_errorbar(aes(ymax = gpmeanACC + (1*SE_acc), ymin =gpmeanACC -(1*SE_acc)), position = dodge, width=.25) + facet_grid(.~bkType) + 
  ylab("mean ACC") + 
  coord_cartesian(ylim = c(80,100)) +
  scale_fill_grey()

```

#### 3-way ANOVA: Accuracy ~ 2 bkType x 2 swProb x 2 trialType
```{r}
z = ezANOVA(data = gpCondM1
            , dv = meanACC
            , wid = sbjId
            , within = .(bkType, swProb, trialType)
            , within_full = .(bkType, swProb, trialType)
            , type = 3
            , detailed = TRUE)
print(z)

```
#### 2-way ANOVA: Accuracy ~ 2 swProb x 2 trialType [cued condition only]
```{r}
z = ezANOVA(data = gpCondM1[gpCondM1$bkType=="cued",]
            , dv = meanACC
            , wid = sbjId
            , within = .(swProb, trialType)
            , within_full = .(swProb, trialType)
            , type = 3
            , detailed = TRUE)
print(z)

```
#### 2-way ANOVA: Accuracy ~ 2 swProb x 2 trialType [choice condition only]
```{r}
z = ezANOVA(data = gpCondM1[gpCondM1$bkType=="choice",]
            , dv = meanACC
            , wid = sbjId
            , within = .(swProb, trialType)
            , within_full = .(swProb, trialType)
            , type = 3
            , detailed = TRUE)
print(z)

```

#### Figure 3: Voluntary task-switching rate: 2 run x 2 swProb
```{r Figure3, fig.width=4.5, fig.height=4}
df <- gpCondM3 %>% select(-tskRatio)
colnames(df)[colnames(df)=="swRate"] <- "M"
LnMSE_swRate <- getWSSE(df)

RunXSwRate <- gpCondM3 %>%
  group_by(runId, swProb) %>% 
  summarise(gpmeanSwRate = mean(swRate), SE_rate = LnMSE_swRate) 

RunXSwRate  %>%
  ggplot(aes(x=runId, y = gpmeanSwRate*100, fill = swProb)) + 
  geom_col(position = dodge) + 
  geom_errorbar(aes(ymax = gpmeanSwRate*100 + (1*SE_rate*100), ymin =gpmeanSwRate*100 -(1*SE_rate*100)), 
                position = dodge, width=.25) + 
  ylab("mean Switch Rate(%)") + 
  coord_cartesian(ylim = c(30,50)) +
  scale_fill_grey()


```


#### ANOVA: switch rate ~ 2 run x 2 swProb

```{r}
z = ezANOVA(data = gpCondM3
            , dv = swRate
            , wid = sbjId
            , within = .(runId, swProb)
            , within_full = .(runId, swProb)
            , type = 3
            , detailed = TRUE)
print(z)


paired_t_pval <-gpCondM3 %>% filter(runId=="9") %>% summarise(pval_ttest = t.test(swRate~swProb, data=., paired = TRUE)$p.value)

print(paired_t_pval)


```

## Additional analyses 

#### Figure 4: Voluntary task-switching rate: 4 run x 2 swProb
```{r Figure4, fig.width=4.5, fig.height=4}
df <- gpCondM4 %>% select(-tskRatio)
colnames(df)[colnames(df)=="swRate"] <- "M"
LnMSE_swRate <- getWSSE(df)

RunXSwRate <- gpCondM4 %>%
  group_by(runId_half, swProb) %>% 
  summarise(gpmeanSwRate = mean(swRate), SE_rate = LnMSE_swRate) 

RunXSwRate  %>%
  ggplot(aes(x=factor(runId_half, labels=c("8.1","8.2","9.1","9.2")), y = gpmeanSwRate*100, fill = swProb)) + 
  geom_col(position = dodge) + 
  geom_errorbar(aes(ymax = gpmeanSwRate*100 + (1*SE_rate*100), ymin =gpmeanSwRate*100 -(1*SE_rate*100)), 
                position = dodge, width=.25) + 
  xlab("run_half") + 
  ylab("mean Switch Rate(%)") + 
  coord_cartesian(ylim = c(30,50)) +
  scale_fill_grey()

```
#### Figure 5:Task Ratio: 2 run x 2 swProb

```{r Figure5, fig.width=4.5, fig.height=4}

df <- gpCondM5 
colnames(df)[colnames(df)=="tskRatio"] <- "M"
LnMSE_tRatio <- getWSSE(df)

bkTypeXtskRatio <- gpCondM5 %>%
  group_by(bkType, swProb) %>% 
  summarise(gpmeanTratio = mean(tskRatio), SE_rate = LnMSE_tRatio) 

bkTypeXtskRatio  %>%
  ggplot(aes(x=bkType, y = gpmeanTratio*100, fill = swProb)) + 
  geom_col(position = dodge) + 
  geom_errorbar(aes(ymax = gpmeanTratio*100 + (1*SE_rate*100), ymin =gpmeanTratio*100 -(1*SE_rate*100)), 
                position = dodge, width=.25) + 
  xlab("bkType") + 
  ylab("% of Task 1") + 
  coord_cartesian(ylim = c(40,60)) +
  scale_fill_grey()

y1 <- gpCondM5 %>% filter(swProb=="sw25%") %>% select(tskRatio)
y2 <- gpCondM5 %>% filter(swProb=="sw75%") %>% select(tskRatio)


paired_t_pval_25 <-gpCondM5 %>% filter(swProb=="sw25%") %>% summarise(pval_ttest = t.test(tskRatio~bkType, data=., paired = TRUE)$p.value)
print(paired_t_pval_25)

paired_t_pval_75 <-gpCondM5 %>% filter(swProb=="sw75%") %>% summarise(pval_ttest = t.test(tskRatio~bkType, data=., paired = TRUE)$p.value)
print(paired_t_pval_75)


```

